%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{fontawesome5}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}

{\Huge \textbf{Stanislav Makarov}}

\vspace{4pt}

{\large Senior QA Automation Engineer \textbar\ Python \textbar\ SDET}

\vspace{4pt}

Moscow, Russia \textbullet\ Open to Relocation

\vspace{6pt}

\small
+7 993 250-39-60 \textbar\
\href{mailto:takahiroMushashii@proton.me}{takahiroMushashii@proton.me}
\textbar\
\href{https://github.com/chyioIshi}{GitHub}
\textbar\
\href{https://linkedin.com/in/chyioIshi}{LinkedIn}
\textbar\
\href{https://t.me/makarovsvv}{Telegram}

\end{center}

\section{Summary}
    \resumeSubHeadingListStart
        {QA Automation Engineer / SDET with 3+ years of experience developing automated
        testing frameworks, testing infrastructure and integration testing solutions
        for distributed microservice platforms.
        
        Specialized in Python automation, REST API, gRPC, Kafka, Kubernetes,
        CI/CD and test infrastructure development.
        
        Currently working as a Senior QA Automation Engineer at Ozon.
        Previously designed and implemented a Python-based testing ecosystem
        including API/UI frameworks, FastAPI mock services,
        CI/CD pipelines and more than 1,200 automated tests
        for a microservice architecture at Alfa-Bank.}
    \resumeSubHeadingListEnd

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Programming:}
Python, SQL \\

\textbf{Test Automation:}
pytest, Playwright, Nuke, Allure TestOps, Jira Zephyr \\

\textbf{Backend:}
FastAPI, requests, Pydantic v2, Beanie ODM, PyMongo, kafka-python \\

\textbf{API \& Integration:}
REST API, gRPC, GraphQL, SOAP, Kafka, OpenAPI \\

\textbf{Databases:}
PostgreSQL, MongoDB, Valkey \\

\textbf{DevOps:}
Git, GitLab CI, Jenkins, Docker, Kubernetes, OpenShift, Helm, uv \\

\textbf{Observability:}
ELK Stack, Kibana, Prometheus, Grafana \\

\textbf{Architecture:}
Microservices, SOA, Event-Driven Architecture, Distributed Systems

}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Ozon}{May 2026 -- Present}
        {Senior QA Automation Engineer}{Employee Profile Ozon Job}

        \resumeItemListStart

            \resumeItem{\textbf{Project:} Employee Profile — distributed platform responsible for employee profile management, financial information, shifts, courses data and status models. Built on gRPC, REST APIs, Kafka, Kubernetes and sharded PostgreSQL.}

            \resumeItem{Develop and maintain end-to-end, API and integration tests using Python, pytest and the company's internal Nuke testing framework.}
            
            \resumeItem{Extend the existing automation framework, improving maintainability, readability and long-term scalability of the test suite.}
            
            \resumeItem{Automate regression testing for newly delivered platform functionality, reducing manual testing effort.}
            
            \resumeItem{Design and implement integration tests for services communicating through REST APIs, gRPC and Kafka.}
            
            \resumeItem{Investigate failures in distributed test environments, perform root cause analysis and collaborate closely with developers to resolve issues.}
            
            \resumeItem{Validate distributed system behavior using Kubernetes, GitLab CI, Valkey and sharded PostgreSQL databases.}
            
            \resumeItem{Participate throughout the software development lifecycle to ensure reliable delivery of new platform functionality.}

        \resumeItemListEnd

    \resumeSubheading
        {Alfa-Bank}{Mar. 2025 -- May 2026}
        {Senior QA Automation Engineer / Python Tooling Developer}
        {FX Derivatives Platform}
        
        \resumeItemListStart
        
            \resumeItem{\textbf{Project:} Distributed foreign exchange derivatives platform supporting forwards, swaps and spot transactions for corporate customers. Microservice architecture built around REST APIs, Kafka and Kubernetes.}
            
            \resumeItem{Developed a FastAPI-based mock service for emulating external systems, enabling isolated integration testing and flexible negative testing scenarios.}
            
            \resumeItem{Built an internal Python service (Zeep, SOAP, REST API, MongoDB) for automated test user provisioning through the ESB, reducing test data preparation time from \textbf{1--2 days to approximately 10 minutes}.}
            
            \resumeItem{Designed and implemented a Jenkins CI/CD pipeline (Groovy) for automated test execution, Allure reporting and release validation.}
            
            \resumeItem{Built from scratch a Python automation framework supporting API, integration and UI testing for a distributed microservice platform.}
            
            \resumeItem{Automated up to \textbf{90\%} of testing for newly developed functionality, including integration, contract and UI test suites.}
            
            \resumeItem{Introduced structured JSON logging with trace identifiers and request metadata, significantly simplifying defect investigation and troubleshooting.}
            
            \resumeItem{Performed production issue analysis using ELK Stack, Kibana, Prometheus and Grafana.}
            
            \resumeItem{Worked extensively with Kubernetes, including Pods, Services, Deployments, Ingresses, Helm Charts and log analysis during system validation and incident investigation.}
            
            \resumeItem{Applied Shift Left Testing practices by reviewing business requirements and technical designs before implementation.}
        
        \resumeItemListEnd

    \resumeSubheading
        {Sber}{Oct. 2023 -- Mar. 2025}
        {QA Automation Engineer}
        {Salute Virtual Assistant}
        
        \resumeItemListStart
        
            \resumeItem{\textbf{Project:} AI-powered virtual assistant for investment and savings products integrated with GigaChat and internal banking services.}
            
            \resumeItem{Increased automated test coverage from \textbf{65\% to 80\%} by developing additional unit and integration tests.}
            
            \resumeItem{Refactored the existing automation framework using software design patterns, improving maintainability and reducing technical debt.}
            
            \resumeItem{Automated validation of an AI intent-classification model, identifying a critical discrepancy between DEV and PROD environments before release.}
            
            \resumeItem{Increased overall automation coverage from \textbf{60\% to 90\%}, significantly reducing regression testing time.}
            
            \resumeItem{Developed integration tests for microservices communicating through Kafka and REST APIs.}
            
            \resumeItem{Mentored junior QA engineers and interns in test automation and CI/CD practices.}
        
        \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{DevMirror}
\href{https://github.com/chyioIshi/DevMirror}{\raisebox{0.2ex}{\footnotesize\faGithub}}
$|$
\emph{Python, FastAPI, MongoDB, Kafka, Docker}}
{}

\resumeItemListStart

\resumeItem{Designed and implemented a universal mock service for integration testing of distributed microservice systems.}

\resumeItem{Built using Domain-Driven Design (DDD) and Clean Architecture principles.}

\resumeItem{Implemented dynamic request matching, scoped mocks, side effects, request logging and Kafka integration.}

\resumeItem{Developed an extensible side-effect engine supporting HTTP callbacks, PostgreSQL, MongoDB, Redis and Kafka providers.}

\resumeItem{Implemented GitHub Actions CI pipeline with Ruff linting and automated validation.}

\resumeItemListEnd

\resumeSubHeadingListEnd



\section{Education}

    \resumeSubHeadingListStart
    
    \resumeSubheading
    {MIREA — Russian Technological University}
    {Moscow, Russia}
    {B.Sc. in Laser Engineering and Laser Technologies}
    {}
    
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
